---
title: "README"
author: "Rasmus Kirkegaard"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: github_document
always_allow_html: true
---

# ONT-yield-tracker
Community sourced tracking of nanopore yields. Are flowcells getting better?

Recently had several Nanopore PromethION flowcells going beyond 200 Gbp and wondered whether this is a common trend.


 * Report your flowcell yields here: [Google form](https://forms.gle/nmUqXLYKG3DxP3SLA)
 * See the reported values in this [Google sheet](https://docs.google.com/spreadsheets/d/1nnnyTM5DiRpobnvqFs0ag48_qqbuEmebVqI_UV5evr8/)




```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(scipen = 10)
```

```{r  echo=FALSE,message=FALSE,results='asis'}
library(tidyverse)
library(gsheet)
library(scales)
d<-gsheet2tbl('https://docs.google.com/spreadsheets/d/1nnnyTM5DiRpobnvqFs0ag48_qqbuEmebVqI_UV5evr8/edit?usp=sharing')

```

## Pores available at QC

```{r echo=FALSE,message=FALSE}
d %>% ggplot(aes(x =`Flowcell type`,y=`Pores at QC`))+geom_boxplot()+expand_limits(y=0)
```

## Data volumes vs pores at QC

```{r echo=FALSE,message=FALSE}
d %>% ggplot(aes(x=`Pores at QC`,y=`Estimated yield (Gbp)`,col=`Flowcell type`))+geom_point()+expand_limits(x=0,y=0)
```

## Most reported flowcells

```{r echo=FALSE,message=FALSE}
d %>% group_by(`SoMe handle (claim your flowcell fame)`) %>% summarise(n=n()) %>% 
  mutate(`SoMe handle (claim your flowcell fame)`=fct_reorder(`SoMe handle (claim your flowcell fame)`, n)) %>%
  ggplot(aes(x=`SoMe handle (claim your flowcell fame)`,y = n))+geom_col()+coord_flip()
```

